### 2013-09-27 manuscripts/dpp-msbayes/dpp-msbayes.tex
Finishing draft of methods for dpp ms; starting results.

\subsection*{Assessing model-choice behavior and robustness}
Following the simulation-based approach of \citet{Oaks2012}, we characterize
the behavior of several models under the ideal conditions where the
data are generated from parameters drawn from the same prior distributions used
for analysis (i.e., the prior is correct).
We selected four model priors for these analyses (Table~\ref{tabPriors}):
(1) A model to represent the original \msb model, \modelOld, with
priors
$\divTimeIndexVector \sim \priorOld$,
$\divTime{} \sim U(0,10)$,
$\ancestralTheta{} \sim U(0, 0.05)$,
and
$\descendantThetaMean{} \sim U(0, 0.05)$;
(2) a Dirichlet-process prior model, \modelDPP, with priors
$\divTimeIndexVector \sim \priorDPP{\sim Gamma(2,2)}$,
$\divTime{} \sim Exp(0.3464)$,
$\ancestralTheta{} \sim Exp(40)$,
and
$\descendantTheta{}{} \sim Exp(40)$;
(3) a model with uniform prior probability over unordered divergence models,
\modelUniform, with priors
$\divTimeIndexVector \sim \priorUniform$,
$\divTime{} \sim Exp(0.3464)$,
$\ancestralTheta{} \sim Exp(40)$,
and
$\descendantTheta{}{} \sim Exp(40)$;
and
(4) a model with the \msb prior on unordered divergence models, but with
exponential priors on nuisance parameters,
\modelUshaped, with priors
$\divTimeIndexVector \sim \priorOld$,
$\divTime{} \sim Exp(0.3464)$,
$\ancestralTheta{} \sim Exp(40)$,
and
$\descendantTheta{}{} \sim Exp(40)$.
The exponential prior on divergence time used in models \modelDPP,
\modelUniform, and \modelUshaped was selected to have the same variance as the
uniform prior in model \modelOld.
The exponential prior on population size used in models \modelDPP,
\modelUniform, and \modelUniform was selected to have the same mean as the
uniform prior in model \modelOld.
All of the models were the same in other respects, with three free \myTheta{}
parameters for each population pair, two uniformly distributed ($beta(1,1)$)
\bottleScalar{}{} parameters per pair, no migration, no recombination,
and unordered divergence models.
For all of our simulations, we used a simulated data structure of eight
population pairs, with a single 1000 base-pair locus sampled from 10
individuals from each population.

For each of the four models, we generated $1\e6$ samples from the prior, and
simulated 50,000 pseudo-replicate datasets, also drawn from the prior.
We then analyzed each of the replicate datasets using the, retaining a
posterior sample from its respective prior.
A GLM-regression adjusted posterior was also estimated from each of the
posterior samples.
To assess the robustness of each of the four models, we also analyzed the
pseudo-replicate datasets simulated under the other three models.
Overall, for each model, we produced 200,000 posterior estimates,
50,000 from the replicate datasets simulated under that model,
and 150,000 estimated from the replicate datasets simulated under the
other three models.

@@

\subsection*{Assessing power}

>>>>

\subsection*{Assessing model-choice behavior and robustness}
Following the simulation-based approach of \citet{Oaks2012}, we characterize
the behavior of several models under the ideal conditions where the
data are generated from parameters drawn from the same prior distributions used
for analysis (i.e., the prior is correct).
We selected four model priors for these analyses (Table~\ref{tabPriors}):
(1) A model to represent the original \msb model, \modelOld, with
priors
$\divTimeIndexVector \sim \priorOld$,
$\divTime{} \sim U(0,10)$,
$\ancestralTheta{} \sim U(0, 0.05)$,
and
$\descendantThetaMean{} \sim U(0, 0.05)$;
(2) a Dirichlet-process prior model, \modelDPP, with priors
$\divTimeIndexVector \sim \priorDPP{\sim Gamma(2,2)}$,
$\divTime{} \sim Exp(0.3464)$,
$\ancestralTheta{} \sim Exp(40)$,
and
$\descendantTheta{}{} \sim Exp(40)$;
(3) a model with uniform prior probability over unordered divergence models,
\modelUniform, with priors
$\divTimeIndexVector \sim \priorUniform$,
$\divTime{} \sim Exp(0.3464)$,
$\ancestralTheta{} \sim Exp(40)$,
and
$\descendantTheta{}{} \sim Exp(40)$;
and
(4) a model with the \msb prior on unordered divergence models, but with
exponential priors on nuisance parameters,
\modelUshaped, with priors
$\divTimeIndexVector \sim \priorOld$,
$\divTime{} \sim Exp(0.3464)$,
$\ancestralTheta{} \sim Exp(40)$,
and
$\descendantTheta{}{} \sim Exp(40)$.
We selected the exponential prior on divergence time used in models \modelDPP,
\modelUniform, and \modelUshaped to have the same variance as the
uniform prior in model \modelOld.
We selected the exponential prior on population size used in models \modelDPP,
\modelUniform, and \modelUniform to have the same mean as the uniform prior in
model \modelOld, so that all four models have the same \myTheta{C} and thus the
same units of time.
All of the models were the same in other respects, with three free \myTheta{}
parameters for each population pair, two uniformly distributed ($beta(1,1)$)
\bottleScalar{}{} parameters per pair, no migration, no recombination,
and unordered divergence models.
For all of our simulations, we used a simulated data structure of eight
population pairs, with a single 1000 base-pair locus sampled from 10
individuals from each population.

For each of the four models, we generated $1\e6$ samples from the prior, and
simulated 50,000 pseudo-replicate datasets, also drawn from the prior.
We then analyzed each of the replicate datasets using the, retaining a
posterior sample from its respective prior.
A GLM-regression adjusted posterior was also estimated from each of the
posterior samples \citep{Leuenberger2010}.
To assess the robustness of each of the four models, we also analyzed the
pseudo-replicate datasets simulated under the other three models.
Overall, for each model, we produced 200,000 posterior estimates,
50,000 from the replicate datasets simulated under that model,
and 150,000 estimated from the replicate datasets simulated under the
other three models.

@@

\subsection*{Assessing power}
We evaluated the power of the same four models (Table~\ref{tabPriors}) to
detect random variation in divergence times using methods similar to
\citet{Oaks2012}.
For all of our power simulations, we used a simulated data structure identical
to that of the empirical dataset of Philippine vertebrates analyzed by
\citet{Oaks2012}, which consists of 22 pairs of populations.
For each of the four models, we generated $2\e6$ samples from the prior.
We then generated pseudo-observed datasets from three series of models.
One series of models, which we denote \powerSeriesOld, is identically
distributed as \modelOld except that the divergence times for each of the 22
pairs of populations are randomly drawn from a series of uniform distributions,
$U(0, \divt{max})$, where \divt{max} was set to: 0.2, 0.4, 0.6, 0.8, 1.0, and
2.0, in \globalcoalunit generations.
A second series of models, \powerSeriesUniform, are identically distributed as
\modelUniform except that the 22 divergence times are randomly drawn from the
same series of uniform priors as above.
The third series of models, \powerSeriesUniformExp, is also identically
distributed as \modelUniform except that the 22 divergence times are randomly
drawn from a series of of exponential distributions: $Exp(17.3205)$,
$Exp(8.6603)$, $Exp(5.7735)$, $Exp(4.33013)$, $Exp(3.4641)$, and $Exp(1.7321)$.
These exponential distributions have the same variance as their uniform
counterparts in the first two series of models.

For each of the six models in each of the three series of models, we simulated
1000 pseudo-replicate datasets (18,000 datasets in total).
We then analyzed each replicate dataset under all four prior models
(Table~\ref{tabPriors}), producing 72,000 posterior estimates, each with 1000
samples.
We also estimated a GLM-regression adjusted posterior from each of the
posterior samples \citep{Leuenberger2010}.

\section*{Results}
